MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-20 paper.Rmd
Updated paper.

Energy flows through society enable economic activity and facilitate human flourishing.
To understand economic growth and human well-being, 
the field of energy analysis (SEA) evaluates energy flows
from the primary stage 
(coal, oil, natural gas) 
to the final stage
(energy purchased by consumers, such as refined petroleum and electricity)
and ultimately to the useful stage
(heat, mechanical drive, and light),
the last energy before energy services
(such as transport, thermal comfort, and illumination).
Societal exergy analysis (SEA), a variant of energy analysis,
quantifies energy flows as exergy, 
the physical work potential of energy.

>>>>

Energy flows through society enable economic activity and facilitate human flourishing.
To understand economic growth and human well-being, 
the field of energy analysis evaluates energy flows
from the primary stage 
(coal, oil, natural gas) 
to the final stage
(energy purchased by consumers, such as refined petroleum and electricity)
and ultimately to the useful stage
(heat, mechanical drive, and light),
the last energy before energy services
(transport, thermal comfort, and illumination).
Societal exergy analysis (SEA), an extension of energy analysis,
quantifies energy flows as exergy, 
the physical work potential of energy.
